\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-12 article.tex
Fix some placement

Coalescing joins nodes \(a\) and \(b\) to node \(ab\) preserving the edges of both to maintain soundness.
Since all edges are preserved, the resulting node \(ab\) may be of a much higher degree. Because of this, only strategies that produce a \(k\)-colorable graph are worth considering, as additional spills negate the purpose entirely. One of the  strategies introduced in the Appel text is the \textit{Briggs} strategy  \cite[232]{tiger}, in which nodes \(a\) and \(b\) can be coalesced if and only if the resulting node \(ab\) has \(\leq K\) nieghbors of significant degree  (i.e. \(\geq K\)).

@@

Consider the previous example (Figure \ref{fig:countdown.ll}): when applied with the same \(k=2\) nothing happens regardless of which allocator is used (see Figure \ref{fig:countdown.briggs.dot2} which was generated using the \texttt{briggs} allocator). This is because although the \texttt{\%c1} and \texttt{\%c2} nodes are not in interference, both neighbors of \texttt{\%c2} are of significant degree (\(\mathit{deg}(\texttt{\%cn}) = 2 \geq 2\) and \(\mathit{deg}(\texttt{\%argc}) = 3 \geq 2\)). 
Therefore they don't satisfy the Briggs criteria, and are not coalesced, resulting in the same interference graph as the \texttt{simple} allocator in Figure \ref{fig:countdown.dot}.
But for some \(k \geq 2\), now there are fewer than \(k\) significant neighbors of \texttt{\%c2} (and \texttt{\%c1}), meaning the two can be coalesced, with the resulting node \texttt{\%c1, \%c2} having two neighbors of insignificant degree.

\begin{figure}[H]
     \centering
   \begin{minipage}[b]{0.50\linewidth}
     \centering
     \includesvg[height=10.9em]{countdown.briggs2}
     \caption{\texttt{build -{}- -t dot -a briggs -n 2}}\label{fig:countdown.briggs.dot2}
   \end{minipage}
   \begin{minipage}[b]{0.33\linewidth}
     \centering
     \includesvg[height=8.em]{countdown.briggs}
     \caption{\texttt{-a briggs -n 3}}\label{fig:countdown.briggs.dot}
   \end{minipage}
\end{figure}

\noindent The purpose is only to assign the same registers to different variables. You don't need to note down information about blocks etc.

>>>>

Coalescing joins nodes \(a\) and \(b\) to node \(ab\) preserving the edges of both to maintain soundness.
Since all edges are preserved, the resulting node \(ab\) may be of a much higher degree. Because of this, only strategies that produce a \(k\)-colorable graph are worth considering, as additional spills negate the purpose entirely. One of the  strategies introduced in the Appel text is the \textit{Briggs} strategy  \cite[232]{tiger}, in which nodes \(a\) and \(b\) can be coalesced iff the resulting node \(ab\) has \(\leq K\) nieghbors of significant degree  (i.e. \(\geq K\)).

@@

Consider the previous example (Figure \ref{fig:countdown.ll}): when applied with the same \(k=2\) nothing happens regardless of which allocator is used (see Figure \ref{fig:countdown.briggs.dot2} which was generated using the \texttt{briggs} allocator). This is because although the \texttt{\%c1} and \texttt{\%c2} nodes are not in interference, both neighbors of \texttt{\%c2} are of significant degree (\(\mathit{deg}(\texttt{\%cn}) = 2 \geq 2\) and \(\mathit{deg}(\texttt{\%argc}) = 3 \geq 2\)). 
Therefore they don't satisfy the Briggs criteria, and are not coalesced, resulting in the same interference graph as the \texttt{simple} allocator in Figure \ref{fig:countdown.dot}.
But for some \(k \geq 2\), now there are fewer than \(k\) significant neighbors of \texttt{\%c2} (and \texttt{\%c1}), meaning the two can be coalesced, with the resulting node \texttt{\%c1, \%c2} having two neighbors of insignificant degree as can be seen in Figure \ref{fig:countdown.briggs.dot}.
\begin{figure}[H]
     \centering
   \begin{minipage}[b]{0.50\linewidth}
     \centering
     \includesvg[height=10.9em]{countdown.briggs2}
     \caption{\texttt{build -{}- -t dot -a briggs -n 2}}\label{fig:countdown.briggs.dot2}
   \end{minipage}
   \begin{minipage}[b]{0.33\linewidth}
     \centering
     \includesvg[height=8.em]{countdown.briggs}
     \caption{\texttt{-a briggs -n 3}}\label{fig:countdown.briggs.dot}
   \end{minipage}
\end{figure}

\noindent The purpose is only to assign the same registers to different variables, which stands to benefit from less \texttt{mov} instructions being used.
%. You don't need to note down information about blocks etc.
